FoRTE baseline

### 2019-03-26 analysis/paper/paper.Rmd
Add radiation profile analysis

```{r, include = FALSE}
lai_10yr_cap <- paste(
  "ED2 leaf area index (LAI) predictions by plant functional type."
)
```

@@

>>>>

```{r captions, include = FALSE}
lai_10yr_cap <- paste(
  "ED2 leaf area index (LAI) predictions by plant functional type."
)

rad_barplot_cap <- paste(
  "Comparison of radiation profiles under two-stream and multiple scatter",
  "canopy radiative transfer models."
)
```

Different model configurations produce significantly different ecological trajectories.

@@

```{r rad_prof, fig.cap = rad_barplot_cap, fig.dim = c(5, 7)}
readd(rad_lineplot)
```
